---
title: "Unit 02 assignment"
author: "Stacey Smith"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 1. Put the following questions into RMarkdown as headers (or subheaders if youre making question numbers headings). Be sure to answer the questions underneath each header. 

## What is a basic workflow for reproducible research?

1. Data Gathering
2. Data Analysis
3. Results Presentation

## What are five practical tips for making research reproducible?

1. Document everything! 
2. Everything is a (text) file. 
3. All files should be human readable. 
4. Explicitly tie your files together. 
5. Have a plan to organize, store, and make your files available.

##	Give an example of how you might implement each tip.

1. Explain or comment every step of the process. In R run the sessionInfo command.
2. Make sure I save all my information in a text file.
3. Make sure I insert comments throughout my research.
4. I will use the commands in Table 2.1 to tie together my research files.
5. I will use GitHub.

##	Which one of these do you think will be the most difficult?

Explicitly tie your files together. 

#------------------------------------------------------------------------------------------------------------------------------------------
# 2. Download and complete air_hist.R code from the Files Tab on 2DS.  You will build scatter plots using the plot function.

```{r}
# Take only Temp columns
Temperature <- airquality$Temp
hist(Temperature)

# Histogram with added parameters
hist(Temperature,
     main="Maximum daily temperature at La Guardia Airport",
     xlab="Temperature in degrees Fahrenheit",
     xlim=c(50,100),
     col="darkmagenta",
     freq=FALSE
)
```

## Plots

```{r pressure, echo=TRUE}
#plot(pressure)
plot(x=airquality$Month, y=airquality$Temp,main = "Temperature by Month", xlab = "Month", ylab = "Temperature by Month")   # How are the Month and temperature measurements relate?

plot(x=airquality$Temp, y=airquality$Ozone,main = "Temperature vs Ozone", xlab = "Temperature", ylab = "Ozone")   # How are the Ozone and temperature measurements relate?
```

#3. Download and complete knit_cars.Rmd in the Files tab on 2DS. 

```{r cars}
summary(cars)
```

```{r cars_plot, echo=FALSE}
plot(cars)
```

## Including Plots
```{r pressure_data}
summary(pressure)
```

You can also embed plots as default, for example:
<!--
TODO: Assignment 2: 3A, complete the following scatter plot. 
The x axis is pressure, while the y axis is temperature
Please title the graph "Temperature vs Pressure"
-->
```{r pressure_plot, echo=TRUE}
#plot(pressure, )
plot(x=pressure, main = "Pressure vs Temperature", xlab = "Pressure", ylab = "Temperature")   # Temperature vs Pressure?
```

Now flip it!

<!--
TODO: Assignment 2: 3B, complete the following scatter plot:
x axis is pressure, y axis is temperature,
Label the x axis as "Pressure" and the y axis as "Temperature", 
Title the graph as "Pressure vs Temperature"
-->

```{r pressure_plot2, echo=TRUE}
plot(x=pressure, main = "Pressure vs Temperature", xlab = "Temperature", ylab = "Pressure",log="y")   # Pressure vs Temperature?
```
