---
title: "Unit3Assignment"
author: "Stacey Smith"
date: "9/17/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Steps to make directory and clone repository

```{r}
#1.mkdir Assignment 
#2.cd Assignment
#3.git clone "https://github.com/awesomedata/awesome-public-datasets.git"
```

## 2. Data Summary

2.	Data Summary: From this aforementioned cloned repo, please extract titanic.csv.zip.  To be clear, this does not have to be done in Git or command line. </br> 
a.	In R, please read in titanic.csv via either read.table() or read.csv(), assigning it to df.  This dataset follows the passengers aboard the Titanic, including their fees paid, rooms rented, and survivorship status.</br> 


```{r}
setwd("/SMU/MSDS_6306_Doing_Data_Science/Week3/Assignment/awesome-public-datasets/Datasets")
df <- read.csv("/SMU/MSDS_6306_Doing_Data_Science/Week3/Assignment/awesome-public-datasets/Datasets/titanic.csv",header = TRUE)
summary(df)
table(df$Sex)
mean(df$Age,na.rm = TRUE)
mean(df$Fare,na.rm = TRUE)
mean(df$Survived,na.rm = TRUE)
```
## Plots for Question 2
```{r, echo=TRUE}
barplot(table(df$Sex),ylim=c(0,600),main='Fequency of Males and Females',xlab = 'Sex',ylab = 'Fequency', col = c('pink','blue'))
```

## 3. Functions Building
```{r sleep}
sleep_function <- function(){
median_age <- median(sleep$Age,na.rm = TRUE)
min_duration_sleep <- min(sleep$Duration, na.rm = TRUE)
max_duration_sleep <- max(sleep$Duration, na.rm = TRUE)
mean_rses <- mean(sleep$RSES, na.rm = TRUE)
sd_rses <- sd(sleep$RSES, na.rm = TRUE)
rses_mean_div = mean_rses/5
sd_rses_div = sd_rses/5
range_sd = range(min_duration_sleep,max_duration_sleep,na.rm = TRUE)
range2 = diff(range_sd)
df_sleep = data.frame(median_age,rses_mean_div,sd_rses_div,range2)
names(df_sleep) <- c("MedianAge", "SelfEsteem", "SE_SD","DurationRange")
round(df_sleep, digits = 2)
}
```
```{r}
setwd("/SMU/MSDS_6306_Doing_Data_Science/Week3/Assignment/awesome-public-datasets/Datasets")
sleep <- read.csv("/SMU/MSDS_6306_Doing_Data_Science/Week3/Assignment/awesome-public-datasets/Datasets/sleep_data_01.csv",header = TRUE)
sleep_function()
```
## 4 and 5. FiveThirty Eight Data
```{r fivethirtyeight, echo=TRUE}

##Column names of each column and count
#install.packages("fivethirtyeight")
library(fivethirtyeight)
df <- data.frame(college_recent_grads)
names(df)
ncol(df)
## of data sets in the package
d <- data(package = "fivethirtyeight")
d$results[, "Item"]
##assign it to use later
nm <- d$results[, "Item"]
data(list = nm, package = "fivethirtyeight")
##get dimensions of each dataset
lapply(mget(nm), dim)
##Generate a count of each unique majory category
major_count <-sapply(df, unique)
```

## Link to GitHub
https://github.com/quedogf94/SMU-MSDS/tree/master/MSDS_6306_Doing_Data_Science/Week3/Assignment


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
